Interactive Curvature Tensor Visualization on Digital Surfaces\thanks{This work has been mainly funded by XXXXXXX research grants.}

### 2015-10-21 latex/article.tex

Using the hierachical nature of the mipmap texture, we could also
consider hierarchical decompositions of either $B_R(\vx)$
(Fig.~\ref{fig:approx2}-$a$) or $B_R(\vx)\cap\Shape$
(Fig.~\ref{fig:approx2}-$b$). The idea would be to decompose the
regions into mipmap cells of different resolution in order to limit
the number of texture access (important bottleneck on GPU hardwares)
and to get better approximated quantities. Note that for the scenario
in Fig.~\ref{fig:approx2}-$b$, there is no approximation (\wrt the
regular grid case) since  geometrical moments are additive quantities.
\begin{figure}
  \begin{center}
    \subfigure[]{\includegraphics[width=5cm]{figs/approx-bh}}
    \subfigure[]{\includegraphics[width=5cm]{figs/approx-ada}}
  \end{center}
  \caption{Adaptive approximation of the integration using a
    hierarchical decomposition of the ball $B_R(\vx)$ $(a)$, or a decomposition of $B_R(\vx)\cap\Shape$.}
  \label{fig:approx2}
\end{figure}

\subsection{Realtime computation on GPU}
\begin{itemize}
\item   Variante 1 : hierarchique avec précalcul cells
\item   Variante 2 : reg avec autoraffinement
\end{itemize}

>>>>

Using the hierachical nature of the mipmap texture, we could also
consider hierarchical decompositions of either $B_R(\vx)$
(Fig.~\ref{fig:approx2}-$a$) or $B_R(\vx)\cap\Shape$
(Fig.~\ref{fig:approx2}-$b$). The idea would be to decompose the
regions into mipmap cells of different resolution in order to limit
the number of texture access (important bottleneck on GPU hardwares)
and to get better approximated quantities. Note that the scenario in
Fig.~\ref{fig:approx2}-$b$, is clearly the best approach: the
volume is exact  (\wrt the regular grid case) since geometrical moments
are additive quantities, and the number of texture fetches is  optimal
at this point.

\begin{figure}
  \begin{center}
    \subfigure[]{\includegraphics[width=5cm]{figs/approx-bh}}
    \subfigure[]{\includegraphics[width=5cm]{figs/approx-ada}}
  \end{center}
  \caption{Adaptive approximation of the integration using a
    hierarchical decomposition of the ball $B_R(\vx)$ $(a)$, or a decomposition of $B_R(\vx)\cap\Shape$.}
  \label{fig:approx2}
\end{figure}

\subsection{Per Vertex Realtime Computation on GPU}

We describe here two different visualization pipeline on GPU that will
be evaluated in the next section.

\paragraph{Hierarchical decomposition}  As discussed above,

\paragraph{Dynamic refinement}

\begin{itemize}
\item   Variante 1 : hierarchique avec précalcul cells
\item   Variante 2 : reg avec autoraffinement
\end{itemize}
